---
title: "Car Inusrance Calculator"
author: "Ossama Embarak"
date: "10/2/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Outlines

**Introduction**

This is the RStudio shiny framework developed as a course project for Coursera 's Emerging Digital Items course on Data Science Specialization. The application built is a basic calculator of interest.

**Course project requirements**

The specifications of the course project for this application are as follows: 
Some type of input (widget: textbox, radio button, checkbox, ...) Some activity on the ui data in sever. R Some reactive output shown as a result of server measurements You must also provide adequate documentation to enable a beginner user to use your program. The documentation should be on the New website itself. Don't post to an external connection. 


## Application - Widgets

The shiny app for this project is a basic car insurance calculator. It contains the following widgets: 

1.	InputField – To enter car price value 

2.	sliderInput – for years of manufacturing 

3.	sliderInput – for insurance period 

4.	Selectinput- for insurance type {Full, Half, against others}

5.	actionButton – a button to calculate the insurance value for the given details.



## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

